\triplebox{cnn chelsea claimed first silverware english domestic season jose mourinho first trophy second spell charge 2 0 win tottenham hotspur wembley sunday. deflected efforts either side halftime chelsea captain john terry leading scorer diego costa dashed tottenham hopes london league cup final. chelsea suffered chastening christmas defeat opposition english premier league harry kane starring promising young english striker kept largely quiet showpiece occasion. first half saw tottenham edge possession carry attacking threat dane christian eriksen free kick rattling chelsea crossbar. chances either side open play short supply free kick chelsea went ahead break.ian delivery right brushed danny rose head fell invitingly terry whose shot went net taking deflection eric dier. tottenham might felt hard done sense injustice would deepened 56 minutes cesc fabregas found costa left firm strike took another wicked deflection time walker credited goal leave goalkeeper hugooris chance. seemed take sting tottenham challenge although [\dots{}]}{new clinton english premier title title. chelsea mourinho chelsea beat chelsea hotspur. 0.. chelsea terry says chad david game. chelsea chelsea chelsea 2 1 win win london win...l. chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea chelsea}{chelsea wins english league cup wembley. jose mourinho team beats tottenham hotspur 2 0 wembley. john terry kyle walker goal chelsea. man city loses 2 1 liverpool miss chance close chelsea top epl.}
